### 2023-10-15 sections/2-methods.tex
some more minor changes to synthetic data sections and results discussion

To elaborate, we start with an original dataset $X$ from the ANN-benchmark suite, a user-specified noise tolerance $\epsilon$, and a mutliplier $m$.
For each datum $x \in X$, we create $m$ new data points within a distance $\epsilon$ of $x$. To construct a synthetic data point $x'$, we choose $d$ random numbers 
$r_1, r_2, \cdots r_d$ in the interval $[-\tfrac{\epsilon}{\sqrt{d}}, \tfrac{\epsilon}{\sqrt{d}}]$ and then add them componentwise to the original datapoint. 
This ensures that any synthetic point is within a distance of $\epsilon$ from a real point in the original dataset.

>>>>

To elaborate, we start with an original dataset $X$ from the ANN-benchmark suite, a user-specified noise tolerance $\epsilon$, and a mutliplier $m$.
For each datum $x \in X$, we create $m$ new data points within a distance $\epsilon$ of $x$. To construct a synthetic data point $x'$, we choose $d$ random numbers 
$r_1, r_2, \cdots , r_d$ in the interval $[-\tfrac{\epsilon}{\sqrt{d}}, \tfrac{\epsilon}{\sqrt{d}}]$ and add them componentwise to the original datapoint. 
Since $\sqrt{d \cdot (\tfrac{\epsilon}{\sqrt{d}})^2 } = \sqrt{d \cdot \tfrac{\epsilon^2}{d}}  = \sqrt{\epsilon^2} = \epsilon$, this ensures that any synthetic point is within a distance of $\epsilon$ from a real point in the original dataset.

### 2023-10-15 sections/3-datasets.tex
some more minor changes to synthetic data sections and results discussion

In addition to benchmarks on datasets from the ANN Benchmarks suite, we also benchmarked on synthetic augmentations of these real datasets, using the process described in \ref{subsec:methods:synthetic-data}. In particular, we use a noise tolerance $\epsilon = 0.01$ and explore the scaling behavior as the multiplier $m$ of new points increases. While we explored the scaling behavior of CAKES with augmented versions of each dataset in \ref{table:datasets:summary}, we give an in-depth discussion of results for scaling behavior on fashion-mnist, glove-100, gist, and a purely random dataset.

>>>>

In addition to benchmarks on datasets from the ANN Benchmarks suite, we also benchmarked on synthetic augmentations of these real datasets, using the process described in \ref{subsec:methods:synthetic-data}. In particular, we use a noise tolerance $\epsilon = 0.01$ and explore the scaling behavior as the multiplier $m$ of new points increases. While we explored the scaling behavior of CAKES with augmented versions of each dataset in \ref{table:datasets:summary}, we give an in-depth discussion in \ref{sec:results} of results for scaling behavior on fashion-mnist, glove-100, gist, and a purely random dataset.

### 2023-10-15 sections/4-results.tex
some more minor changes to synthetic data sections and results discussion

Notably, we observe that on all datasets, GreedySieve's throughput stays nearly constant as cardinality increases. This observation warrants further investigation, but it is especially promising given that GreedySieve consistently outperforms linear search for high cardinalities and consistently outperforms our other algorithms for $k=100$. 
We also notice an interesting trend with Sieve and Sieve with Separate centers: for all datasets, at both values of $k$, both algorithms exhibit a sharp ``pivot point'' after which throughput starts to increase. 
While we observe that this pivot point seems to be proportional to the value of $k$, as it often occurs at about a multiplier of 4 when $k=10$ and a mulitplier of 32 when $k=100$, the reason for this behavior requires further investigation.  
Finally, we reiterate that the variation in performance across our algorithms based on dataset, value of $k$, and cardinality support our use of an autotuning function to select the best choice of algorithm. 
Currently, our autotuning function always uses $k=10$ for its determination, but our observation that the best algorithm differs significantly between small and large values of $k$ suggests that more sophisticated autotuning is necessary.

>>>>

Notably, we observe that on all datasets, GreedySieve's throughput stays nearly constant as cardinality increases. This observation warrants further investigation, but it is especially promising given that GreedySieve consistently outperforms linear search for high cardinalities and consistently outperforms our other algorithms for $k=100$. 
We also notice an interesting trend with Sieve and Sieve with Separate centers: for all datasets, at both values of $k$, both algorithms exhibit a sharp ``pivot point'' after which throughput starts to increase. 
While we observe that this pivot point seems to be proportional to the value of $k$, as it often occurs at about a multiplier of 4 when $k=10$ and a mulitplier of 32 when $k=100$, the reason for this behavior requires further investigation.  
Finally, we reiterate that the variation in performance across our algorithms based on dataset, value of $k$, and cardinality support our use of an autotuning function to select the best choice of algorithm. 
Currently, our autotuning function always uses $k=10$ for its determination, but our observation that the best algorithm often differs between small and large values of $k$ suggests that more sophisticated autotuning is necessary.
